% TODO 
% NUMBER PUBS and others
% bold my name
% add dates when submitted, resubmitted
% ORIGINAL RESEARCH
% METHODOLOGY
% EDITORIAL
% CONFERENCE

%  I:\My Dropbox\personal\Employment\CV\Ivan-Hanigan-CV.tex
%%% A template to produce a nice-looking Curriculum Vitae.
%%% Kieran Healy <kjhealy@gmail.com>
%%% Most recent version is at 
%%%
%%% ------------------------------------------------------------------------
%%% Requirements (should be included in a modern tex distribution):
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

% \documentclass[11pt]{article}
\documentclass[a4paper,11pt]{article}
%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Ivan C. Hanigan}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{Canberra, Australia}
\def\myaddress{15 Follett Street, Scullin}
\def\myemail{ivan.hanigan@anu.edu.au}
%\def\myweb{http://www.kieranhealy.org}
\def\myphone{02 61257767, 0428265976}
\def\myfax{02 6125 0740}
\def\myversion{}
\def\myrevision{}


\def\myaffiliation{Australian National University}
\def\myauthor{Ivan C. Hanigan}
\date{\today} % not used (revision control instead)
\def\mykeywords{Ivan, Hanigan, Ivan Hanigan, Vita, CV, Resume, Human Ecology}

%%%------------------------------------------------------------------------  
%%% Git version tracking 
%%%------------------------------------------------------------------------

%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
% \input{vc}

%%%------------------------------------------------------------------------
%%% Required style files
%%%------------------------------------------------------------------------
\usepackage{url,fancyhdr}
\usepackage{revnum} % for reverse-numbered publications (revnumerate environment) if needed.

%% needed for xelatex to work
\usepackage{fontspec}
\usepackage{xunicode}

%% color for the links 
\usepackage[usenames,dvipsnames]{color}

%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	urlcolor=BlueViolet,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at 
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
%\setromanfont[Mapping={tex-text},Numbers={OldStyle},Ligatures={Common}]{Myriad} 
%\setsansfont[Mapping=tex-text,Colour=AA0000]{Myriad Pro}
% \setmonofont[Mapping=tex-text,Scale=0.9]{Pragmata} 


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

% revnum see http://www.enel.ucalgary.ca/People/vigmond/latex/latex.html
%this counter must be manually 
% set so that the last publication is labelled as 1
%\newcounter{totalnumpubs}
%\setcounter{totalnumpubs}{15}

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyfoot{}
\rhead{{\scriptsize\thepage}}

%% git revision control footer 
% \rfoot{\texttt{\scriptsize \VCRevision\ on \VCDateTEX}} % git revision info inserted via external script -- see docs for vc package for details. comment out this line if you're not using vc, and also remove the \input{vc} line above.

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
% \flushright {\footnotesize \href{http://nceph.anu.edu.au}{National Centre for Epidemiology \\ and Population Health} \\ Australian National University, \\ \vspace{-0.05in} Canberra, \textsc{ACT} 0200}  
 \flushright {\footnotesize \vspace{0.22in} 15 Follett Street \\ Scullin \\ Canberra \\ \textsc{Australia} 2614}  
   
\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize \textbf{\today} \bigskip \\ Phone: \myphone \\ 
  Fax: \myfax  \\ 
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}}} \\
%  {\scriptsize  \texttt{\href{\myweb}{\myweb}}}
\end{minipage}


\medskip

%% Name 
\noindent{\Large {\textsc{Ivan C Hanigan.}}}
% September 2012.}}}

%\noindent{\Large {\textsc{August 2011}}}

\reversemarginpar

\medskip       

\medskip
\marginhead{Date of Birth}	
{\vskip 0.1em}
\noindent 8th September, 1977

\marginhead{Family}	
{\vskip 0.4em}
\noindent Married with two children

\marginhead{Nationality}
{\vskip 0.6em}
\noindent Australian

% \marginhead{Objective}
% %\noindent Multidisciplinary data manager and analyst seeking to expand on over 10 years research experience with scientific work that will complement my part-time PhD.
% {\vskip 0.7em}
% \noindent To use my skills in data management and analysis, particularly spatial analysis, to improve sustainable public health.  

%% Appointments
\medskip
\marginhead{Summary}
{\vskip 0.3em}
\noindent I am a multidisciplinary data manager and analyst with over
10 years experience at one of Australia's leading universities. I have
primarily worked in Environmental Epidemiology where I have honed my
skills in manipulation of large databases and multivariate regression
modelling.  I also have experience of
scenario-based forecasting in climate change risk assessments.
%The integration of gridded, point-source and area-based administrative data has become a speciality.  

I have been the lead author on four papers in international journals,
and contributing author on numerous journal papers, reports and
conference presentations.
%I am also undertaking a multi-disciplinary PhD, on a part time basis.\\

I have used the Data Documentation Initiative (DDI)
international standard for metadata since 2009 to ensure
the data management system is suitably documented and maintained
throughout the Data Analysis Lifecycle.  

My programming skills include the R language for statistical computing
and graphics, SQL using Postgres and PostGIS.  I also have experience
with QGIS, ArcGIS, Stata, Oracle-XE, Linux (Ubuntu, Centos, RHEL).

%\medskip

% \noindent Please also check my online CV for an updated publication list at \\
% \emph{\href{http://www.mendeley.com/profiles/ivan-hanigan/}{http://www.mendeley.com/profiles/ivan-hanigan}}
%\vspace{0.01in}} 

%\medskip
\marginhead{Appointments}

%\medskip

\bigskip
{\vskip 0.2em}
\noindent\emph{\textbf{Australian National University} \vspace{0.01in}}

2008--Present.  Data Manager, National Centre for Epidemiology and \\
\ind Population Health (NCEPH). 

2008--2009. Data Analyst, Environment, Climate and Health Group \\
\ind (NCEPH).

%\begin{itemize}
%\item 2008--Present.  Data Manager, National Centre for Epidemiology and Population Health (NCEPH). 
%\item 2008--2009. Data Analyst, Environment, Climate and Health Group (NCEPH).
%\end{itemize}
\medskip
\noindent\emph{\textbf{University of Tasmania} \vspace{0.01in}}

2008--2011. Data Manager and Analyst, Bushfire Smoke, Heatwaves and \\
\ind Health Project,    School of Plant Science.

\medskip

\noindent\emph{\textbf{Charles Darwin University} \vspace{0.01in}}

2006--2007.  Data Manager and Analyst, Bushfire Smoke and Health \\
\ind Project, School of Environmental Research.

\medskip

\noindent\emph{\textbf{Australian National University} \vspace{0.01in}}

2001--2006.  Research Assistant  Environmental Epidemiology Group (NCEPH).

\medskip

% \noindent\emph{\textbf{Australian National University} \vspace{0.01in}}

% 2000.  Laboratory Animal Technician, John Curtin School of Medical \\
% \ind Research.

%\bigskip
%% Education
\clearpage
\marginhead{Education}
{\vskip 0.3em}
\ind \textbf{\emph{Australian National University \vspace{0.01in}}}

2009--Present: Part-time PhD entitled \emph{Disentangling Health Effects of} \\
\ind \emph{Environmental Change from Social Factors}, NCEPH and CSIRO. \\
Panel: Colin Butler, Philip Kokic, Rohan Nelson, Steven McEachern.
%\vspace{-0.1in}  \\

%\begin{itemize}
 	%\item \small Winner of the American Sociological Association's Dissertation
% 	  Award for 2002.
%\end{itemize}      


1998-2005: Bachelor of Arts in Geography and Human Ecology, First \\
\ind Class Honours, School of Resources, Environment and Society. ANU.


\medskip

%\bigskip
 
%% Publications
\marginhead{{\vskip 0.4em}Papers}
\medskip
%\noindent\emph{Book \vspace{0.01in}}

%\ind  Kieran Healy. 2006. \emph{\href{http://www.lastbestgifts.com}{Last Best Gifts: Altruism and the Market for Human Blood and Organs}}. Chicago:~University of Chicago Press. \vspace{-0.075in}
 
\normalsize

%\bigskip
%\noindent\emph{Journal articles \vspace{0.05in}}
 
%% Use revnumerate environment if numbered publications are needed. 
%% (Include it above in the preamble).
\renewcommand{\labelenumi}{\textsc{a}\theenumi.}
\begin{revnumerate}
%\begin{revnumerate}[\value{totalnumpubs}]
%\ind Hall, G, Hanigan, IC, Dear, KBG, and Vally, H. 2010. ``\href{http://journals.cambridge.org/abstract_S0950268810001901.}{The influence of weather on community gastroenteritis in Australia}.'' \emph{Epidemiology and Infection.} 

\item \textbf{Hanigan IC}, Butler CD, Kokic PN and Hutchinson MF. \emph{Suicide and drought in New South Wales, Australia, 1970-2007}.  Proceedings of the National Academy of Science USA 2012;109(35).\\
doi: 10.1073/pnas.1112965109.

\item  Vally H, Peel M, Dowse GK, Cameron S, Codde JP, \textbf{Hanigan IC} and Lindsay MD. \emph{Geographic Information Systems used to describe the link between the risk of Ross River virus infection and proximity to the Leschenault estuary, WA}. Australian and New Zealand Journal of Public Health 2012;36(3). doi:10.1111/j.1753-6405.2012.00869.x

\item Johnston FH, \textbf{Hanigan IC}, Henderson SB, Morgan, GG and Bowman, DMJS. \emph{Extreme air pollution events from bushfires and dust storms and their association with mortality in Sydney, Australia 1994-2007}.  Environmental Research 2011;111(6). doi:10.1016/j.envres.2011.05.007

\item Johnston FH, \textbf{Hanigan IC}, Henderson SB, Morgan GG, Portner T, \\
 Williamson GJ and Bowman DMJS. \emph{Creating an integrated historical record of extreme particulate air pollution events in Australian cities from 1994 to 2007}. Journal of the Air and Waste Management Association 2011;61(4). doi:10.3155/1047-3289.61.4.390

\item Hall GV, \textbf{Hanigan IC}, Dear KBG and Vally H. \emph{The influence of weather on community gastroenteritis in Australia}. Epidemiology and Infection 2011;139(6). doi:10.1017/S0950268810001901

\item Edwards F, Dixon J, Friel S, Hall G, Larsen K, Lockie S, Wood B, Lawrence M, \textbf{Hanigan IC}, Hogan A and Hattersley L. \emph{Climate change adaptation at the intersection of food and health}. Asia-Pacific Journal of Public Health 2011;23(2). doi:10.1177/1010539510392361 

\item Bambrick H, Woodruff R and \textbf{Hanigan IC}. \emph{Climate change could threaten blood supply by altering the distribution of vector-borne disease: an Australian case-study}.  Global Health Action 2009;2. doi:10.3402/gha.v2i0.2059

\item Johnston FH, \textbf{Hanigan IC} and Bowman DMJS. \emph{Pollen loads and allergic rhinitis in Darwin, Australia: A potential health outcome of the grass-fire cycle}. Ecohealth 2009;6(1). doi: 10.1007/s10393-009-0225-1

\item \textbf{Hanigan IC}, Johnston FH and Morgan GG. \emph{Vegetation fire smoke, indigenous status and cardio-respiratory hospital admissions in Darwin, Australia, 1996-2005}. Environmental Health 2008;7(42). doi:10.1186/1476-069X-7-42

\item \textbf{Hanigan IC} and Johnston FH. \emph{Respiratory hospital admissions were associated with ambient airborne pollen in Darwin, Australia, 2004-2005}. Clinical and Experimental Allergy 2007;37(10). doi:10.1111/j.1365-2222.2007.02800.x

\item Johnston FH, Bailie RS, Pilotto LS and \textbf{Hanigan IC}. \emph{Ambient biomass smoke and cardio-respiratory hospital admissions in Darwin, Australia}. BMC Public Health 2007;7(1). doi:10.1186/1471-2458-7-240

\item D’Souza RM, Bambrick H, Kjellstrom T, Kelsall L, Guest C and \textbf{Hanigan IC}. \emph{Seasonal variation in acute hospital admissions and emergency room presentations among children in the ACT}. Journal of Paediatrics and Child Health 2007;43(5). doi:10.1111/j.1440-1754.2007.01080.x

\item Dear KBG, Ranmuthugala G, Kjellstrom T, Skinner C and \textbf{Hanigan IC}. \emph{Effects of temperature and ozone on daily mortality experienced in France during the August 2003 heat wave}. Archives of Environmental and Occupational Health 2006;60(4). PMID:17214291

\item \textbf{Hanigan IC}, Hall GV and Dear KBG. \emph{A comparison of methods for calculating population exposure estimates of daily weather for health research}. International Journal of Health Geographics 2006;5(1). doi:10.1186/1476-072X-5-38

\item Nicholls N, Butler C and \textbf{Hanigan IC}. \emph{Inter-annual rainfall variations and suicide in New South Wales, Australia, 1964-2001}. International Journal of Biometeorology 2006;50(3). doi:10.1007/s00484-005-0002-y
\end{revnumerate}
%\newpage
%\bigskip 


{\vskip 0.4em}
\marginhead{{\vskip 0.2em}Manuscripts Submitted}
\medskip
\renewcommand{\labelenumi}{\textsc{b}\theenumi.}
\begin{revnumerate}

\item Johnston FH, \textbf{Hanigan IC}, SB Henderson and Morgan GG. \emph{Effect of air pollution control on death rates in Launceston, Australia, 1994-2007: an Intervention study}.  Revised and resubmitted to The British Medical Journal on 24 September 2012. 

\item Powers JR, Dobson AJ, Berry HL, Graves AM, \textbf{Hanigan IC} and Loxton D. \emph{Mental health and drought: results from a 12 year prospective cohort study of Australian women}. Submitted to The Lancet on 4 October 2012. 

\item O'Brien LV, Berry HL, Coleman C and \textbf{Hanigan IC}. \emph{Specific pattern of drought associated with worse mental health in rural areas but not in urban areas of Australia}.  Submitted to British Journal of Psychiatry on October 26, 2012. 
\end{revnumerate}
%\ind Martin, KL, Hanigan, IC, Morgan, GG, Henderson, SB, Johnston, FH. Air pollution events from vegetation fires and their association with hospital admissions in Sydney, Newcastle and Wollongong, Australia 1994-2007. Submitted to International Journal of Epidemiology. 

%\ind Morgan, G, Hanigan, IC, Wilson, L, Jalaludin, B, Johnston, F, Abu-Rayya, H, Gaskin, C, Broome, R. The impact of extreme heat on mortality and morbidity in five climatic regions of New South Wales: A case crossover analysis.

% data
{\vskip 0.4em}
\marginhead{{\vskip 0.4em}Data Publications}
\medskip
%\ind The paper Hanigan et al 2006 is accompanied by 3 data collections: \\
\renewcommand{\labelenumi}{\textsc{c}\theenumi.}
\begin{revnumerate}
\item http://researchdata.ands.org.au/meteorological-data-for-australian-postal-areas \\
\item http://researchdata.ands.org.au/postal-areas-grouped-into-15-climatic-regions-with-population-densities \\
\item http://researchdata.ands.org.au/map-of-bureau-of-meteorology-monitoring-stations-in-nsw-overlayed-on-postal-area 

\end{revnumerate}
%
%\bigskip
\marginhead{{\vskip 0.4em}Published Abstracts}
\medskip
%\noindent\emph{Other journal publications \vspace{0.05in}}
\renewcommand{\labelenumi}{\textsc{d}\theenumi.}
\begin{revnumerate}

\item \textbf{Hanigan IC}, Johnston FH, Morgan GG, Dingle JK and Bowman DMJS.  \emph{Assessing the Relationship Between Exposure to Vegetation Fire Smoke and Hospital Admissions when Empirical Air Quality Measurements are Limited: Darwin, Australia, 1996-2005}.  Epidemiology 2008;19(6) Supplement:S266 [ISEE 2008 Conference Abstracts Supplement]

\item D'Souza RM, Becker NG, Hall G, Kjellstrom T, Bambrick H, Kelsall L, \textbf{Hanigan IC} and Guest C. \emph{Climatic factors associated with hospitalisations and emergency room presentations for diarrhoea in children}. Epidemiology 2005;16(5):S60 [ISEE 2005 Conference Abstracts Supplement].

\item D'Souza RM, Becker NG, Kjellstrom T, Bambrick H, Woodruff R, Kelsall L, \textbf{Hanigan IC} and Guest C. \emph{Influence of climatic factors on hospitalisations and emergency room presentations for asthma and other (non-asthma) respiratory conditions in children}. Epidemiology 2005;16(5):S50 [ISEE 2005 Conference Abstracts Supplement].

\end{revnumerate}

%\newpage
%\noindent\emph{Reports \vspace{0.05in}}
%\bigskip 
\medskip
%\marginhead{{\vskip 0.4em}Reports}
\marginhead{Reports}
{\vskip 0.4em}
\renewcommand{\labelenumi}{\textsc{e}\theenumi.}
\begin{revnumerate}

\item Bambrick H, Woodruff R and \textbf{Hanigan IC}. \emph{Effective emissions targets needed to protect Australia’s blood supply}.  The Australia Institute Policy Brief No. 11 2010

\item McMichael AJ, Berry H, Butler C, Capon A, Dear KBG, \textbf{Hanigan IC}, Harley DO, Kjellstrom T, Lucas R and Strazdins L. 2009. \emph{Assessing the scale and nature of health vulnerability to climate change}.  Background report for Campbell-Lendrum D and Bertollini R, Protecting health from climate change: global research priorities.  World Health Organisation, Geneva.

\item Bambrick H, Dear KBG, Woodruff R, \textbf{Hanigan IC} and McMichael AJ.  \emph{The impacts of climate change on three health outcomes: temperature-related mortality and hospitalisations, salmonellosis and other bacterial gastroenteritis, and population at risk from dengue}.  Garnaut Climate Change Review, Commonwealth of Australia 2008.

\item Berry H, Kelly B, \textbf{Hanigan IC}, Coates J, McMichael AJ, Welsh J and Kjellstrom T. \emph{Rural mental health impacts of climate change}. Garnaut Climate Change Review 2008.

\item D'Souza RM, Hennessy K, Cope M, McMichael AJ, Page C, Whetton P, Physick B and \textbf{Hanigan IC}. \emph{A scoping study of the impact of climate change on air pollution over Sydney}. Consultancy for NSW Environmental Protection Agency. 2003.

\item \textbf{Hanigan IC}.  \emph{Hotspots of Pathogens in Drinking Water Catchments: Case Study of Googong Catchment}.  ECOWISE Environmental Pty. Ltd. and ActewAGL, Canberra. 2003.

\end{revnumerate}
\bigskip

%% Presentations
\medskip
\marginhead{{\vskip 0.4em}Conference Posters and Presentations}
\medskip
\renewcommand{\labelenumi}{\textsc{f}\theenumi.}
\begin{revnumerate}

\item Johnston FH, \textbf{Hanigan IC}, Henderson SB, Morgan GG and Bowman, DMJS. \emph{The association between mortality and air pollution events from bushfires and dust storms in Sydney, 1994-2007}. Royal College of Physicians Annual Scientific Meeting, Darwin,  2011. [Poster]

\item Morgan G, \textbf{Hanigan IC}, Wilson L, Abu-Rayya H, Gaskin C, Johnston F, Lloyd G, Broome R, and Jalaludin B. \emph{The effects of heat waves on mortality and hospitalisation in Sydney, Australia 1994-2009}. 23th Congress of the International Society for Environmental Epidemiology, Barcelona, 2011. [Poster].

\item Johnston FH, \textbf{Hanigan IC}, Henderson SB, Morgan GG and Bowman DMJS. \emph{Preliminary results from the Australian landscape fire smoke project}. International Society for Environmental Epidemiology, Annual Scientific Meeting, Seoul Korea Sept 2010. [Poster]

\item Bambrick H, Dear KBG and \textbf{Hanigan IC}.  \emph{Deaths in a sunburnt country: Differential mortality responses to temperatures in a 'hot' country}. IOP Conference Series Earth and Environmental Science, 6 142013, 2009. [Poster]

\item Banwell C, Dixon J, Bambrick H, Hinde S, Kjellstrom T, Lucas R and \textbf{Hanigan IC}. \emph{Socio-cultural reflections on comfort and heat in Australia with implications for climate change adaptation}. IOP Conference Series Earth and Environmental Science, 6 572023, 2009. [Poster]

\item Johnston FH and \textbf{Hanigan IC}.  \emph{Tropical plant pollens and allergic rhinitis}.  The Thoracic Society of Australia and New Zealand Annual Scientific Meeting.  Darwin, 6-7 April 2009. [Poster]
% \href{http://www.thoracic.org.au/asm2009pa01.pdf}{Link}.

\item McMichael AJ and \textbf{Hanigan IC}. \emph{Drought and drying: The human dimension. Risks to Wellbeing and Health. Drought – Past and Future}. ANU Water Initiative. ANU, Canberra. Nov 14, 2008. [Oral]
%\href{http://www.water.anu.edu.au/events/dpf/program.php}{Link}. 

\item \textbf{Hanigan IC}, Johnston FH, Morgan GG, Dingle JK and Bowman DMJS. \emph{Assessing the relationship between exposure to vegetation fire smoke and hospital admissions when empirical air quality measurements are limited: Darwin, Australia, 1996-2005}. Joint Annual Conference of the International Society for Environmental Epidemiology and International Society of Exposure Analysis. Pasadena, California, Oct 2008. [Oral]

\item \textbf{Hanigan IC} and Nicholls N. \emph{Geo-coded Australian meteorological data: sources, content, uses}. Climate Change And Health Short Course: Research and policy issues in relation to health impacts and adaptations.  Australian National University, Canberra. 4-6 December 2007. [Oral]

\item Johnston FH, \textbf{Hanigan IC} and Morgan GG. \emph{Vegetation fire smoke, indigenous status and cardio-respiratory hospital admissions in Darwin, Australia, 1996-2005}. 14th International Union of Air Pollution Prevention and Environmental Protection Associations World Congress Brisbane 9 - 13 September 2007. [Oral]
% \href{http://www.iuappa2007.com/abstract/152.htm}{Link}.

\item Physick B, Cope M, Lee S, Hurley P, Dear KBG, D’Souza RM and \textbf{Hanigan IC}. \emph{Optimum exposure fields for epidemiology and health forecasting}. 28th NATO/CCMS International Technical Meeting on Air Pollution Modelling and its Application. Liepzig, Germany. 15-19 May, 2006. [Poster]

\item \textbf{Hanigan IC}. \emph{Integrating health, population and environmental data across long time-series}. The workshop on Environmental Stress and Impacts on Health. Australian National University, Canberra. November 24-25, 2005. [Oral]

\item \textbf{Hanigan IC}. \emph{Applying Geographical Information Systems (GIS) to health and demographic data: A case study of Sydney}. The 2nd Innovations (Atmospheric Environment and Health Collaboration) Workshop: National and sub-national data sources in environmental health. The Australian National University, Canberra. May 5-6, 2003. [Oral]

\item \textbf{Hanigan IC}, Whiteway T, Balzer I, Wade A, Page D. \emph{Identifying potential “hotspots” for pathogens in the Googong Catchment}, Australian Water Association 20th Convention, 6-10 April 2003, Perth. [Oral]

\item Page DW, \textbf{Hanigan IC}, van Leeuwen JA, Spark KM and Mulcahy DE.  \emph{Assessment of the treatability of dissolved organic matter (DOM) from terrestrial and freshwater sources, with alum}, Australian Water Association 20th Convention, 6-10 April 2003, Perth. [Poster]


\end{revnumerate}



%\newpage

\marginhead{{\vskip 0.4em}Media}
\medskip
%\ind I have experience talking with Journalists about the findings of my scientific publications for a general audience. 
\renewcommand{\labelenumi}{\textsc{g}\theenumi.}
\begin{revnumerate}

\item \emph{\href{http://news.anu.edu.au/?p=16631}{http://news.anu.edu.au/?p=16631}}

%\noind 
\item \emph{\href{http://www.abc.net.au/science/articles/2012/08/14/3567208.htm}{http://www.abc.net.au/science/articles/2012/08/14/3567208.htm}}

%\noind 
\item \emph{\href{http://www.livescience.com/22314-drought-may-increase-suicide-risk.html}{http://www.livescience.com/22314-drought-may-increase-suicide-risk.html}}

\item \emph{Meet the Researcher} June-July 2012 edition of the National Climate Change Adaptation Research Network Human Health Newsletter.
\end{revnumerate}

\marginhead{{\vskip 0.4em}Peer Reviewing}
\medskip
%\noindent I have experience with the peer review of journal papers:
\renewcommand{\labelenumi}{\textsc{h}\theenumi.}
\begin{revnumerate}

\item Willocks LJ, et al. (2012). Cardiovascular disease and air pollution in Scotland: no association or insufficient data and study design? BMC Public Health, 12(1), 227. doi:10.1186/1471-2458-12-227.

\item BMC Public Health November 2012 (In progress).

\item Crisis: The Journal of Crisis Intervention and Suicide Prevention, November 2012 (In progress).

\end{revnumerate}

\marginhead{{\vskip 0.4em}Contribution to Teaching and Learning}
\medskip
%\noindent I undertake several additional scholarly activities in addition to my core Data Management related work:
\renewcommand{\labelenumi}{\textsc{i}\theenumi.}
\begin{revnumerate}

\item I have sat on several selection panels for job interviews both at NCEPH and for other Centres at the University.

\item Training in software programming, data analysis and data management for staff and students.

\item I organise weekly topics and speakers for the ANU GIS Forum meetings.

\item I contribute to ANU wide data management meetings with the Australian Data Archives and the National Supercomputer facility.

\item I contributed Drought Severity data to several papers by members of the Collaboration on Drought, Drying and Rural Mental Health.
\end{revnumerate}

\marginhead{{\vskip 0.4em}Technical courses attended}
\medskip
\renewcommand{\labelenumi}{\textsc{j}\theenumi.}
\begin{revnumerate}

\item Computing for Data Analysis, 24 Sep - 27 Oct 2012.  Prof Roger Peng Johns Hopkins Bloomberg School of Public Health, Coursera.

\item Bayesian Hierarchical Modelling of Spatial and Temporal Data, 21-23 November 2011, CSIRO/ANU, Canberra, ACT.

\item Statistical Data and Metadata eXchange (SDMX) standard and tools.  24 March 2010, Australian Bureau of Statistics.

\item Australian Weather and Society Integrated Studies Workshop.  29th – 2nd February 2007.  Emergency Management Australia, Mount Macedon, VIC.

\item Spatial Analysis in Environmental and Social Epidemiology.  5th  - 8th  September 2005. The Australian National University, Canberra.

\item Formatting long documents in Microsoft Word, 2004, The Australian National University Information Literacy.

\item Endnote Referencing Software training, 2004, The Australian National University Information Literacy.

\item Air Pollution Exposure: measurement, modelling and assessment.  2nd - 3rd  December 2004, The Australian National University, Canberra. 

\item Climate Change and Health: Research Methods and Policy Issues.  29th September – 2nd  October 2003, The Australian National University, Canberra.
\end{revnumerate}

\bigskip

\marginhead{{\vskip 0.4em}Grants}
\medskip
\renewcommand{\labelenumi}{\textsc{k}\theenumi.}
\begin{revnumerate}
\item 2012, A Scientific Workflow System for Assessing and Projecting the Health Impacts of Extreme Weather Events. PI Keith Dear, ANU.	
\item 2011, Dengue Transmission under Climate Change in Northern Australia: Linking Ecological and Population Data. PI David Harley, ANU.	
\item 2010, Suicide and Drought: Understanding Human Impacts of Environmental Change, PI Ivan Hanigan, ANU.	
\item 2010, Climate Change and Rural Communities: Integrated study of physical and social impacts, health risks and adaptive options. PI Anthony McMichael, ANU. 	
\item 2009, I was named as Professional Staff on Understanding the Health Effects of Landscape Burning and Biomass Smoke. PI Prof David Bowman UTAS. 	
\item 2005, Health Forecasting System,	PI Rennie D'Souza, ANU.

\end{revnumerate}

\marginhead{{\vskip 0.4em}Awards}
\medskip  
\begin{revnumerate}
\item Oct 2012 Runner Up, Australian National Data Service eResearch tools for the National Cloud competition.

\item Oct 2006 NCEPH Director’s prize for best publication for the month.

\item June 2003 NCEPH Director’s prize for best presentation at annual student workshop.

\item Jan 2003 Cooperative Research Centre Water Quality and Treatment Summer Scholar.
\end{revnumerate}
\bigskip 

%\newpage

\marginhead{{\vskip 0.9em}Referees}
\medskip

\medskip
\renewcommand{\labelenumi}{\textsc{l}\theenumi.}
\begin{revnumerate}

\item Dr Colin Butler, Epidemiologist, University of Canberra.   Email: colin.butler@canberra.edu.au

\item Dr Keith Dear, Senior Fellow Biostatistics, ANU NCEPH.  Ph: 02 6125 4865, Email: Keith.Dear@anu.edu.au

\item Dr Fay Johnston, Epidemiologist, UTAS Menzies School of Health Research. Ph: 0407612247, Email: Fay.Johnston@utas.edu.au
\end{revnumerate}
\end{document}